Structured Versus Decorated Cospans

### 2020-11-18 cospans.tex
rewrote a bit of introductory stuff on mon Groth

% John Baez, Kenny Courser and Christina Vasilakopoulou
% 2020/11/12 - JB
% 2020/11/17

@@

\begin{thm} \label{thm:equiv}
Suppose $\ca{A}$ has finite colimits and $F\maps(\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor that factors through $\bicat{Rex}$ as an ordinary pseudofunctor. Then the symmetric monoidal double categories $F\lCsp$ of decorated cospans and $_L\lCsp(\inta F)$ of structured cospans are equivalent, where $L \maps \A \to \inta F$ is a left adjoint of the induced Grothendieck opfibration $U\maps \inta F \to \A$.
\end{thm}

@@

In \cite{MV}, the classical Grothendieck construction is generalized to the monoidal setting: lax monoidal structures on a pseudofunctor $F\maps\A\to\Cat$ (called \emph{monoidal opindexed categories}) bijectively correspond to monoidal structures on the total category $\inta F$ such that the induced opfibration is a strict monoidal functor and $\otimes_{\inta F}$ preserves cocartesian liftings (called \emph{monoidal fibrations}). If the monoidal category $\A$ is in fact cocartesian, there is a further correspondence of the two structures with an ordinary pseudofunctor $F\maps\A\to\bicat{MonCat}$ into the 2-category of monoidal categories, strong monoidal functors and monoidal natural transformations.

@@

\begin{thm}
\label{thm:bicat}
Let $\A$ be a category with finite colimits and $F \maps (\A, +) \to (\Cat,\times)$ a symmetric lax monoidal pseudofunctor. Then there exists a symmetric monoidal bicategory $F \mathbf{Csp}$ in which:
\begin{enumerate}
\begin{itemize}
\item objects are those of $\A$,
\item morphisms are $F$-decorated cospans:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$c$};
\node (C) at (2,0) {$b$};
\node (D) at (4,0) {$d \in F(c)$,};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
\item a 2-morphism is a map of cospans in $\A$ 
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0.5) {$c$};
\node (C) at (2,0) {$b$};
\node (E) at (1,-0.5) {$c'$};
\node (D) at (3,0.5) {$d \in F(c)$};
\node (F) at (3,-0.5) {$d' \in F(c')$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(A) edge node[below]{$i'$} (E)
(B) edge node[left]{$h$} (E)
(C) edge node[below]{$o'$} (E);
\end{tikzpicture}
\]
together with a morphism $\tau \maps F(h)(d) \to d'$ in $F(c')$.
\end{enumerate}
\end{itemize}
\end{thm}

>>>>

% John Baez, Kenny Courser and Christina Vasilakopoulou
% 2020/11/17

@@

\begin{thm} \label{thm:equiv}
Suppose $\A$ has finite colimits and $F\maps(\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor that factors through $\Rex$ as an ordinary pseudofunctor. Then the symmetric monoidal double categories $F\lCsp$ of decorated cospans and $_L\lCsp(\inta F)$ of structured cospans are equivalent, where $L \maps \A \to \inta F$ is a left adjoint of the induced Grothendieck opfibration $U\maps \inta F \to \A$.
\end{thm}

@@

In \cite{MV}, the classical Grothendieck construction is generalized to the monoidal setting: given a monoidal category $\A$ there is a bijection between
\begin{itemize}
\item 
\define{monoidal opindexed categories}: lax monoidal pseudofunctors $F\maps\A\to\Cat$
\end{itemize}
and
\begin{itemize}
\item \define{monoidal opfibrations}: opfibrations
$U \maps \X \to \A$ where $\X$ is monoidal, $U$ is strict monoidal, and $\otimes_\X$ preserves cocartesian liftings.
\end{itemize}
If the monoidal structure on $\A$ is in fact cocartesian, there is a further correspondence between either of these structures and ordinary pseudofunctors $F\maps\A\to\bicat{MonCat}$ into the 2-category of monoidal categories, strong monoidal functors and monoidal natural transformations.

@@

\begin{thm}
\label{thm:bicat}
Let $\A$ be a category with finite colimits and $F \maps (\A, +) \to (\Cat,\times)$ a symmetric lax monoidal pseudofunctor. Then there exists a symmetric monoidal bicategory $F \mathbf{Csp}$ in which:
\begin{itemize}
\item objects are those of $\A$,
\item morphisms are $F$-decorated cospans:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$c$};
\node (C) at (2,0) {$b$};
\node (D) at (4,0) {$d \in F(c)$,};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
\item a 2-morphism is a map of cospans in $\A$ 
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0.5) {$c$};
\node (C) at (2,0) {$b$};
\node (E) at (1,-0.5) {$c'$};
\node (D) at (3,0.5) {$d \in F(c)$};
\node (F) at (3,-0.5) {$d' \in F(c')$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(A) edge node[below]{$i'$} (E)
(B) edge node[left]{$h$} (E)
(C) edge node[below]{$o'$} (E);
\end{tikzpicture}
\]
together with a morphism $\tau \maps F(h)(d) \to d'$ in $F(c')$.
\end{itemize}
\end{thm}
